On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-03 MS.tex
Change Fig and table

\documentclass[a4paper,11pt]{article}
\usepackage[osf]{mathpazo}
\usepackage{ms}
\usepackage[]{natbib}
\raggedright

\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
\usepackage{graphicx}
\usepackage[title,titletoc,toc]{appendix}

@@

\subsection*{Dataset construction}

@@

Using the identified boundaries among stages we were able to assign all studies into one of three classes: ``juvenile'', ``sapling'', or ``adult''.  We preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition. Using the above cut-offs we were also able to assign a stage category to studies for which no stage have been distinctly mentioned by the authors (5\% of the data, noted as ``mix'' in Fig. \ref{fig:fig2}). Only 5 of 112 studies were ambiguous on their plant stage attribution. Half of these equivocal cases involved the juvenile category. We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category. The others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors. Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 52 and 50). Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age. Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig. \ref{fig:figA5} model.1. In the main text, we report only results using the standardized categories.

@@

\subsubsection*{Effect size calculation}

@@

\subsubsection*{Stage effect}

@@

\subsubsection*{Sensitivity analysis}

@@

%TODO: I suggest keeping this table, but merging the two right hand columns. The text in the explanation column mostly just repeats material that is presented elsewhere, so best to just say briefly where to find it.
\begin{table}[h!]
\centering
\caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{3cm} p{1cm} p{10cm} p{3cm}}
  \hline
  Quality criteria & Check & Explanations & Addressed in \\
  \hline
  1. Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf    mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), in English. & ``Systematic search'', Table \ref{tab:lit_search} \\
  2. Reporting inclusion/exclusion criteria & yes & Studies included report i) correlation coefficient between growth and trait, ii) the sample size/ number of species, and iii) the size/stage of plants. Studies excluded report correlation within species	& ``Systematic search'' \\
  3. Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. The question addressed in our study concerns the correlation between growth and trait across species, thus the number of species is a better proxy of a study quality than sample size. &	 ``Systematic search'' and  ``Effect size calculation'' \\
 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	``Statistical analyses'', Fig3 \\
 5. Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ (Santos and Nakagawa, 2012) for each trait. &	Appendix D \\
 6. Exploring causes of heterogeneity &	yes &	We explored two causes of variability: the stage and the year of publication & Appendix D, Fig3 \\
 7. Multifactorial analysis of explanatory variable	& yes & We focused on the ``plant stage'' as the main exploratory variable. Yet, the stage variable may be confounded with other explanatory moderators (i.e. growth measurement, experiment type or growth form). Thus, we checked if no one of them would not consistenly be a strongest predictor of the data. We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. & FigA4, FigA6  \\
  8. Testing for publication bias &	yes	& We used funnel plots for a visual assessment. We used the ``trim and fill'' method to estimate the number of studies missing (Duval and Tweedie 2000). We also estimated the Rosenberg’s fail-safe number (Rosenberg 2005). 	&  Appendix D, FigA7\\
  9. Sensitivity analysis &	yes &	We tested how robust are our results to the decision made in the analysis. We calculated effect size using 3 differents dataset: i) an  ``ideal'' dataset, focusing on unstressed conditions exclusively, ii) a ``complete'' dataset reporting all conditions, and iii) a ``reduced dataset'' where multiple responses were condensed into a single average within a trait and within a study. &	Fig3, FigA5 \\
  10.Exploring temporal changes in effect size &	yes	& There may be a confounding effect between the publication year and the stage. Thus, we explored the publication effect on the effect size within each stage for traits where a stage effect had been highlighted (SLA and SM). & Appendix D, FigA9 \\
  11. Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species. &	\\
  12. Specifying the software used &	yes	& R software, code available on Github. & ``Availability of code and data'' \\
 13. Providing reference list of primary studies included in the analysis &	yes &	Available on Github. The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses, `read.bib` corresponds to all the articles (included and excluded) inspected for the meta-analyses.	& ``Availability of code and data'' \\
  14. Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.	& ``Availability of code and data'' \\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[osf]{mathpazo}
\usepackage{ms}
\usepackage[]{natbib}
%\raggedright

\newcommand{\smurl}[1]{\url{#1}}
\usepackage{graphicx}
\usepackage[title,titletoc,toc]{appendix}

@@

\subsection*{Dataset construction}\label{data-construction}

@@

Using the identified boundaries among stages we were able to assign all studies into one of three classes: ``juvenile'', ``sapling'', or ``adult''.  We preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition. Using the above cut-offs we were also able to assign a stage category to studies for which no stage have been distinctly mentioned by the authors (5\% of the data, noted as ``mix'' in Fig. \ref{fig:fig2}). Only 5 of 112 studies were ambiguous on their plant stage attribution. Half of these equivocal cases involved the juvenile category. We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category. The others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors. Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 150). Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age. Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig. \ref{fig:figA5} model.1. In the main text, we report only results using the standardized categories.

@@

\subsubsection*{Effect size calculation}\label{effect-size}

@@

\subsubsection*{Stage effect}\label{stage-effect}

@@

\subsubsection*{Sensitivity analysis}\label{sensitivity-analysis}

@@

%TODO: I suggest keeping this table, but merging the two right hand columns. The text in the explanation column mostly just repeats material that is presented elsewhere, so best to just say briefly where to find it.
\clearpage
\begin{table}[h!]
\centering
\caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{5cm}p{0.8cm}p{9cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed? \\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& We provided complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language and search dates) in sub-section "Phase 2 - Systematic search" in material and method.\\
  2.& Reporting inclusion/exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method. The Bibtex file `read.bib` on Guithub reports all the articles red but laid out because they failed to met our criteria.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variation, and stage as a fixed effect. See details in sub-section "Stage effect" in material and methods. Results are shown in Fig3.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix D.\\
 6.& Exploring causes of heterogeneity & yes &	We explored the effect of stage, and the year of publication (see points 4 and 10 in this list). \\
 7.& Multifactorial analysis of explanatory variable	& yes & We checked if no one of several other explanatory moderators (i.e. growth measurement, experiment type or growth form) would not consistenly be a strongest predictor of the data. We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See FigA4b and FigA6.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method and the Rosenberg’s fail-safe number). See details of methods and results in Appendix D and FigA7\\
  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig3 and FigA5 \\
  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix D and FigA9.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sub-section ``Availability of code and data'' in material and methods\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	See sub-section ``Availability of code and data'' in material and methods. The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses. \\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github. See ``Availability of code and data'', section "Statistical analysis" in material and methods. \\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}
